Efficient implementation of kernel filtering

### 2007-07-03 article/Article.tex
missing table reference
darcs-hash:20070703140948-2fc9d-5b0237a5b52710a1fe406aad0b5b35424ad73650.gz
missing table reference
darcs-hash:20070703141204-2fc9d-70b1992fea85c74c46cdb1593a919e94f2d3678a.gz

\begin{figure}[htbp]
\begin{center}
\subfigure[Mean]{\includegraphics[scale=0.62]{fastRankMean-perfMean}}
\subfigure[Median]{\includegraphics[scale=0.62]{fastRankMean-perfMedian}}
\caption{Execution times for several algorithms of mean filters (a) and
median filters (b).\label{fig:perfRank}}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[Neighborhood size]{\includegraphics[scale=0.62]{boxConvolution-perf2D-large}}
\subfigure[Threads]{\includegraphics[scale=0.62]{boxConvolution-perf_threads-large}}
\caption{Execution times for and increasing kernel size (a), and an increasing number of threads (b).
\label{fig:perfBoxConv}
Results are reported in Table \ref{tab:perfBoxConv}}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[Mean]{\includegraphics[scale=0.62]{fastRankMean-perfMean}}
\subfigure[Median]{\includegraphics[scale=0.62]{fastRankMean-perfMedian}}
\caption{Execution times for several algorithms of mean filters (a) and
median filters (b).\label{fig:perfRank}
Results are reported in Tables \ref{tab:perfRankMean} and  \ref{tab:perfRankMedian}.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[Neighborhood size]{\includegraphics[scale=0.62]{boxConvolution-perf2D-large}}
\subfigure[Threads]{\includegraphics[scale=0.62]{boxConvolution-perf_threads-large}}
\caption{Execution times for and increasing kernel size (a), and an increasing number of threads (b).
\label{fig:perfBoxConv}
Results are reported in Tables \ref{tab:perfBoxConv} and  \ref{tab:perfBoxConv-threads}}
\end{center}
\end{figure}
